Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Victor Chahuneau$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-09 paper/paper.tex
typo

\begin{compactdesc}
\item[\feat{DocLen}] Document length in tokens.
\item[\feat{Punct}] Counts of each punctuation mark. 
\item[\feat{Pron}] Counts of each pronoun.
\item[\feat{Position}] Positional token frequency. We use the counts
  for the first two and last three words before the period in each
  sentence as features. High-weight features for the \emph{second} word include: {\tt ARA:2<,>}; {\tt CHI:2<is>}; {\tt HIN:2<can>}.
\item[\feat{PsvRatio}] The proportion of passive verbs out of all
  verbs.
\item[\feat{CxtFxn}] Contextual function words. \raggedright High-weight features include: {\tt CHI:<some JJ>}; \mbox{\tt HIN:<as VBN>}. 
\item[\feat{Misspell}] Spelling correction edits. \sw{???}. \raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBT<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
\item[\feat{Restore}] Counts of substitutions, deletions and
  insertions of predefined tokens that we restored in the texts. High-weight features include: {\tt CHI:DELWORD<do>}; {\tt GER:DELWORD<on>}; {\tt ITA:DELWORD<be>}  
\end{compactdesc}
\noindent
\Tref{tbl:addfeats} reports the empirical improvement that each of
these brings independently when added to the main features
(\Sref{sec:mainfeats}).

>>>>

\begin{compactdesc}
\item[\feat{DocLen}] Document length in tokens.
\item[\feat{Punct}] Counts of each punctuation mark. 
\item[\feat{Pron}] Counts of each pronoun.
\item[\feat{Position}] Positional token frequency. We use the counts
  for the first two and last three words before the period in each
  sentence as features. High-weight features for the \emph{second} word include: {\tt ARA:2<,>}; {\tt CHI:2<is>}; {\tt HIN:2<can>}.
\item[\feat{PsvRatio}] The proportion of passive verbs out of all
  verbs.
\item[\feat{CxtFxn}] Contextual function words. \raggedright High-weight features include: {\tt CHI:<some JJ>}; \mbox{\tt HIN:<as VBN>}. 
\item[\feat{Misspell}] Spelling correction edits. \sw{???}. \raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBST<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
\item[\feat{Restore}] Counts of substitutions, deletions and
  insertions of predefined tokens that we restored in the texts. High-weight features include: {\tt CHI:DELWORD<do>}; {\tt GER:DELWORD<on>}; {\tt ITA:DELWORD<be>}  
\end{compactdesc}
\noindent
\Tref{tbl:addfeats} reports the empirical improvement that each of
these brings independently when added to the main features
(\Sref{sec:mainfeats}).
